---
title: "Journal"
author: "Taushin Tanvir Shagar"
date: "2020-11-18"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

# Intro to the tidyverse
```{r, code=readLines("C:/Users/sagor/Documents/GitHub/ws20-business-data-science-basics---lab-journal-ttsagor/DS_101/01_getting_started/sales_analysis.R")}
```

# Data Acquisition
```{r, code=readLines("chapter3.R")}
```

# Data Wrangling
In this chapter, large data files are being processed The codes are commented out to avoid running compilation during journal build process All codes are test individually and output this is provide after the section of the code

```{r, code=readLines("chapter4.R")}
```

# Data Visualization
```{r, code=readLines("chapter5.R")}
```